Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Uploading the updated paper

\section{Introduction}
Text summarization is a problem of

\subsection{Abstractive vs Extractive summarization}

Abstractive text summarization allows us to write summaries that are almost as good as those written by humans.

Abstractive text summarization is more challenging, but it is close to what humans do.

Data-driven approach

@@

\subsection{The power of extractive summarization}

Though it will not be the focus of our work, extractive text summarization is dominant in this field and serves as a baseline for abstractive models. Before we move any further, we must understand what makes statistical techniques so powerful.

@@

\section{Data collection and preparation}

@@

\subsection{ROUGE}

The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{kishore-2}.

@@

\subsection{Embedding-based metric}

@@

\[ \text{CAROUGE-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]

@@

\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]

@@

@@

We have tried different methods of text summarization, both extractive (TextRank, TF-IDF) and abstractive (Seq2Seq, SeqGAN).

\subsection{TextRank}
In this research we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score.

\begin{table}[H]
\caption{Example of an abstract generated by our model}

@@

@@

\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} \\
\hline
TextRank & 18.04 & 4.10 & 10.89 \\
LSTM & 0 & 0 & 0 \\
SeqGAN & 0 & 0 & 0 \\
\hline
\end{tabular}
\end{center}
\end{table}

% \subsection{Timeframes}

% \paragraph{Deliverables for the $1^{st}$ evaluation}
% \begin{itemize}
% \item Dataset of papers collected from arXiv
% \item Results of feature extraction
% \item Implementations of the baseline state-of-the-art model and its application to our dataset
% \end{itemize}

% \paragraph{Deliverables for the $2^{nd}$ (final) evaluation}
% \begin{itemize}
% \item Implementation of several discrete GAN models
% \item Evaluation of the created models on our dataset
% \item Paper describing the results of our research
% \end{itemize}

>>>>

\section{Introduction}

@@

\subsection{Abstractive vs extractive summarization}

\paragraph{Extractive text summarization}

\subsection{Abstractive summarization}

\paragraph{Abstractive text summarization} allows us to write summaries that are almost as good as those written by humans. It is closer to what humans do when they write text summaries, but also more complex. T

\subsection{Scientific text summarization}

The problem of summarizing scientific texts is very different from general-purpose text summarization. Every scientific paper starts with an abstract, which by its nature is the summary of a document created by its human-author. This allows us to can create a human-labeled dataset of scientific papers just by separating abstracts from the text body.

@@

\section{Data collection and preparation}
\label{sec:data}

@@

\subsection{ROUGE}
\label{sec:rouge}

The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}.

@@

\subsection{CAROUGE}

@@

\[ \text{CAROUGE-N}(s_i) = \frac{1 - \operatorname*{min}_j ||s_i - c_j||}{k} \]

@@

\[ \text{CAROUGE-N}(s) = \frac1n \sum_{i=1}^n \frac{1 - \operatorname*{min}_j ||s_i - c_j||}{k} \]

@@

Using the same example as in the section \ref{sec:rouge} we can see that CAROUGE score of a decent abstractive summary will be greater than 0.

\[ r = \text{"The great paper"} \]
\[ s = \text{"A wonderful article"} \]
\[ \text{ROUGE}(s) = 0 \]
\[ \text{CAROUGE}(s) = 0.8956 \]

@@

We have tried different methods of text summarization, both extractive (TextRank, RAKE) and abstractive (Seq2Seq, SeqGAN).

\subsection{RAKE}

Rapid Automatic Keyword Extraction algorithm (RAKE)\cite{rose-10} is a keyword extraction algorithm which tries to determine key phrases in a body of text by analyzing the frequency of word appearance and its co-occurance with other words in the text. Its main advantages include  time efﬁciency, operating on individual documents. It can be easily applied to new domains and multiple types of documents. RAKE is very sensitive to unclean data, as it relies on word frequency.

\begin{table}[H]
\caption{Example of an abstract generated by RAKE}

\begin{center}
\begin{tabular}{|p{0.25\linewidth}|p{0.67\linewidth}|}
\hline
\textbf{Title} & The Multivariate Generalised von Mises distribution: Inference and  applications \\
\hline
\textbf{Real abstract} & ...Previously proposed multivariate circular distributions are shown to be special cases of this construction. Second, we introduce a new probabilistic model for circular regression, that is inspired by Gaussian Processes, and a method for probabilistic principal component analysis with circular hidden variables... \\
\hline
\textbf{\makecell[l]{Generated \\ abstract}} & ...many data modelling problems since higher order generalised von mises distributions model circular variables using distributional assumptions probabilistic principal component analysis ppca proposed resulting distribution inherits desirable characteristics paper makes three technical contribu tions multivariate generalised... \\
\hline
\end{tabular}
\end{center}
\end{table}

\subsection{TextRank}
In this research we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score. Unlike RAKE which operates n-grams, TextRank generates summaries using whole sentences. For that reason the generated summaries are more readable.

\begin{table}[H]
\caption{Example of an abstract generated by TextRank}

@@

In the table below you can see the results of our experiments represented by mean scores over all 2000 papers from our dataset.

@@

% \begin{center}
% \begin{tabular}{|l|c|c|c|c|}
% \hline
% \textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{ROUGE-L} & \textbf{CAROUGE-1} \\
% \hline
% TextRank & 18.04 & 4.10 & 10.89 & 0 \\
% RAKE & 8.93 & 1.54 & 7.54 & 0 \\
% Human & 0 & 0 & 0 & 0 \\
% \hline
% \end{tabular}
% \end{center}
% \end{table}

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Model} & \textbf{ROUGE-1} & \textbf{ROUGE-2} & \textbf{CAROUGE-1} \\
\hline
TextRank & 18.04 & 4.10 & 0 \\
RAKE & 8.93 & 1.54 & 0 \\
Human & 0 & 0 & 0 \\
\hline
\end{tabular}
\end{center}
\end{table}
